---
title: 'Data Management & Analysis Final Project'
subtitle: 'Replication and Extention for Acemoglu, Naidu, Restrepo and Robinson (2019)'
author: 
  - "(Name:) Shoya Abe (University ID:) 31B24001"
  - "(Name:) Honoka Ohtani (University ID:) 31B24002"
date: "(Submission Due:) 2025/02/06"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
    number_sections: true
  word_document:
    toc: true
    toc_depth: 3
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{float}
  - \usepackage[table]{xcolor}
---

\newpage

## Setup
  
```{r setup, echo=TRUE, cache=FALSE, warning=FALSE, message=FALSE}
pacman::p_load(
  rmdformats,
  knitr,
  tinytex,
  haven,
  tidyverse,
  kableExtra,
  plm,
  texreg
)

## Global options
options(max.print="75")
opts_chunk$set(fig.align="center",
               echo=TRUE,
               cache=TRUE,
               prompt=FALSE,
               tidy=FALSE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

# About this Report

## Project Type

## Summary of the Paper

### What the problem is

### Why it is important

### How you solve the problem

### What we find

## Data

```{r}
data <- read_dta("data/raw/DDCGdata_final.dta")

# Define the function to summarize the data
summarize_data <- function(data, n = 10) {
  cat("Sample size (number of rows):",
      nrow(data), "\n")
  cat("Number of variables (columns):",
      ncol(data), "\n")
  cat("Variable names (first",
      n, "names):\n")
  print(head(colnames(data), n))
}

summarize_data(data)
```

## Empirical Methods

### Event Study (Figure.1)

### Dynamic Liner Panel Model (Table.2)

# Replication

## Figure.1

### Preprocessing

```{r}
data_f1 <- data %>%
  rename(id = "_ID") %>%
  group_by(id) %>%
  arrange(year) %>%
  mutate(
    prev_dem = dplyr::lag(dem, 1),
    transition = case_when(
      dem == 1 & prev_dem == 0 ~ 1,
      dem == 0 & prev_dem == 0 ~ 0,
      TRUE ~ NA_real_
    ),
    lag1 = dplyr::lag(y, 1),
    lag2 = dplyr::lag(y, 2),
    lag3 = dplyr::lag(y, 3),
    lag4 = dplyr::lag(y, 4)
  ) %>%
  filter(
    !is.na(lag1) &
      !is.na(lag2) &
      !is.na(lag3) &
      !is.na(lag4)
  ) %>%
  ungroup()

for (t in -15:-2) {
  col_name <- paste0("gdpDiff_m", abs(t))
  data_f1 <- data_f1 %>%
    group_by(id) %>%
    arrange(year) %>%
    mutate(!!col_name := dplyr::lag(y, abs(t)) - lag1) %>%
    ungroup()
}

data_f1 <- data_f1 %>%
  mutate(
    gdpDiff_m1 = 0,
    gdpDiff_0  = y - lag1
  )

for (t in 1:30) {
  col_name <- paste0("gdpDiff_p", t)
  data_f1 <- data_f1 %>%
    group_by(id) %>%
    arrange(year) %>%
    mutate(!!col_name := dplyr::lead(y, t) - lag1) %>%
    ungroup()
}

data_f1 <- data_f1 %>%
  filter(!is.na(transition))
```

### Estimation

```{r}
estimateATET <- function(outcome_col) {
  sub_data <- data_f1 %>%
    filter(
      !is.na(.data[[outcome_col]]),
      !is.na(transition)
    )
  if (nrow(sub_data) == 0)
    return(NA)

  year_levels <- sort(unique(sub_data$year))
  sub_data <- sub_data %>%
    mutate(year_factor = factor(year, levels = year_levels))

  control_data <- sub_data %>%
    filter(transition == 0)
  treated_data <- sub_data %>%
    filter(transition == 1)

  if (nrow(control_data) < 2 ||
      length(unique(control_data$year)) < 2)
    return(NA)

  model_formula <- as.formula(
    paste(outcome_col, "~ year_factor - 1")
  )

  control_model <- tryCatch(
    lm(model_formula, data = control_data),
    error = function(e) NULL
  )

  if (is.null(control_model))
    return(NA)

  predicted_outcomes <- tryCatch(
    predict(control_model, newdata = treated_data),
    error = function(e) rep(NA, nrow(treated_data))
  )

  treatment_effects <- treated_data[[outcome_col]] - predicted_outcomes
  mean(treatment_effects, na.rm = TRUE)
}

relative_times <- c(seq(-15, -1), seq(0, 30))
atets <- numeric(length(relative_times))

for (i in seq_along(relative_times)) {
  t_val <- relative_times[i]
  if (t_val < 0) {
    col_name <- paste0("gdpDiff_m", abs(t_val))
  } else {
    col_name <- if (t_val == 0)
      "gdpDiff_0" else paste0("gdpDiff_p", t_val)
  }
  atets[i] <- estimateATET(col_name)
}

results_df <- data.frame(
  RelativeTime = relative_times,
  ATET         = atets
)
```

### Plot

```{r}
figure_1 <- ggplot(results_df, aes(x = RelativeTime, y = ATET)) +
  geom_line(color = "black") +
  scale_x_continuous(breaks = seq(-15, 30, 5)) +
  labs(
    x = "Years around Democratization",
    y = "Change in GDP per capita (log points)"
  ) +
  theme_bw()

ggsave("output/figure_1.pdf",
       width = 14,
       height = 8,
       units = "cm")
```

![Event Study](output/figure_1.pdf)

## Table.1

### Preprocessing

```{r}
var_info <- tibble(
  var = c(
    "gdppercapitaconstant2000us",
    "ginv",
    "tradewb",
    "prienr",
    "secenr",
    "taxratio",
    "mortnew",
    "unrestn",
    "marketref"
  ),
  label = c(
    "GDP per capita",
    "Investment share of GDP",
    "Trade share of GDP",
    "Primary-school enrollment rate",
    "Secondary-school enrollment rate",
    "Tax revenue share of GDP",
    "Child mortality per 1,000 births",
    "Unrest rate",
    "Market reforms index (0–100)"
  )
)

calc_summary <- function(df, var, group_var) {
  df %>%
    filter(!is.na(.data[[var]])) %>%
    group_by({{ group_var }}) %>%
    summarise(
      Observations = n(),
      Mean         = mean(.data[[var]], na.rm = TRUE),
      SD           = sd(.data[[var]], na.rm = TRUE),
      .groups      = "drop"
    ) %>%
    mutate(Variable = var)
}

var_list <- var_info$var
```

### Caliculation

```{r}
summary_table <- lapply(
  var_list,
  function(x) calc_summary(data, x, dem)
) %>%
  bind_rows() %>%
  pivot_wider(
    names_from  = dem,
    values_from = c(Observations, Mean, SD),
    names_glue  = "{.value}_dem{dem}"
  ) %>%
  rename(
    Observations_Nondem = Observations_dem0,
    Mean_Nondem         = Mean_dem0,
    SD_Nondem           = SD_dem0,
    Observations_Dem    = Observations_dem1,
    Mean_Dem            = Mean_dem1,
    SD_Dem              = SD_dem1
  ) %>%
  left_join(
    var_info,
    by = c("Variable" = "var")
  ) %>%
  select(
    label,
    Observations_Nondem,
    Mean_Nondem,
    SD_Nondem,
    Observations_Dem,
    Mean_Dem,
    SD_Dem
  ) %>%
  rename(Variable = label)

colnames(summary_table) <- c(
  "Variable",
  "Observations",
  "Mean",
  "SD",
  "Observations",
  "Mean",
  "SD"
)
```

### Tabulation

```{r}
latex_table <- summary_table %>%
  kbl(
    caption   = "Summary Statistics by Democracy Status",
    format    = "latex",
    booktabs  = TRUE,
    digits    = 2
  ) %>%
  add_header_above(
    c(" " = 1, "Nondemocracies" = 3, "Democracies" = 3)
  ) %>%
  kable_styling(
    latex_options = c("HOLD_position", "striped")
  )

save_kable(latex_table, file = "output/table_1.tex")
```

\input{output/table_1.tex}

## Table.2

### Preprocessing

```{r}
data_t2 <- data %>%
  select(1:30) %>%
  group_by(country_name) %>%
  arrange(year) %>%
  mutate(
    lag1 = dplyr::lag(y, 1),
    lag2 = dplyr::lag(y, 2),
    lag3 = dplyr::lag(y, 3),
    lag4 = dplyr::lag(y, 4),
    lag5 = dplyr::lag(y, 5),
    lag6 = dplyr::lag(y, 6),
    lag7 = dplyr::lag(y, 7),
    lag8 = dplyr::lag(y, 8)
  ) %>%
  ungroup()
```

### Estimation

```{r}
data_m1 <- data_t2 %>%
  drop_na(y, dem, lag1)
data_m1 <- pdata.frame(data_m1,
                       index = c("country_name", "year"))
model_1 <- plm(
  y ~ dem + lag1,
  data   = data_m1,
  model  = "within",
  effect = "twoways"
)

data_m2 <- data_t2 %>%
  drop_na(y, dem, lag1, lag2)
data_m2 <- pdata.frame(data_m2,
                       index = c("country_name", "year"))
model_2 <- plm(
  y ~ dem + lag1 + lag2,
  data   = data_m2,
  model  = "within",
  effect = "twoways"
)

data_m3 <- data_t2 %>%
  drop_na(y, dem, lag1, lag2, lag3, lag4)
data_m3 <- pdata.frame(data_m3,
                       index = c("country_name", "year"))
model_3 <- plm(
  y ~ dem + lag1 + lag2 + lag3 + lag4,
  data   = data_m3,
  model  = "within",
  effect = "twoways"
)

data_m4 <- data_t2 %>%
  drop_na(y, dem, lag1, lag2, lag3, lag4,
          lag5, lag6, lag7, lag8)
data_m4 <- pdata.frame(data_m4,
                       index = c("country_name", "year"))
model_4 <- plm(
  y ~ dem + lag1 + lag2 + lag3 + lag4 +
    lag5 + lag6 + lag7 + lag8,
  data   = data_m4,
  model  = "within",
  effect = "twoways"
)

beta_hat_1  <- coef(model_1)["dem"]
gamma_hat_1 <- coef(model_1)[c("lag1")]
long_run_effect_1 <- beta_hat_1 / (1 - sum(gamma_hat_1))

beta_hat_2  <- coef(model_2)["dem"]
gamma_hat_2 <- coef(model_2)[c("lag1", "lag2")]
long_run_effect_2 <- beta_hat_2 / (1 - sum(gamma_hat_2))

beta_hat_3  <- coef(model_3)["dem"]
gamma_hat_3 <- coef(model_3)[c("lag1", "lag2", "lag3", "lag4")]
long_run_effect_3 <- beta_hat_3 / (1 - sum(gamma_hat_3))

beta_hat_4  <- coef(model_4)["dem"]
gamma_hat_4 <- coef(model_4)[c("lag1", "lag2", "lag3",
                               "lag4", "lag5", "lag6",
                               "lag7", "lag8")]
long_run_effect_4 <- beta_hat_4 / (1 - sum(gamma_hat_4))

lre <- round(
  c(
    long_run_effect_1,
    long_run_effect_2,
    long_run_effect_3,
    long_run_effect_4
  ),
  3
)
print(lre)

pers1 <- sum(coef(model_1)[2])
pers2 <- sum(coef(model_2)[2:3])
pers3 <- sum(coef(model_3)[2:5])
pers4 <- sum(coef(model_4)[2:9])
pers <- round(
  c(pers1, pers2, pers3, pers4),
  3
)
print(pers)

dem_shortrun <- coef(model_1)["dem"]
lag1_mod1 <- coef(model_1)[2]
effect1 <- dem_shortrun
effect2 <- (effect1 * lag1_mod1) + dem_shortrun
effects_mod1 <- c(effect1, effect2)

for (i in 3:30) {
  eff <- (effects_mod1[i-1] * lag1_mod1) + dem_shortrun
  effects_mod1 <- c(effects_mod1, eff)
}
eff_25_1 <- effects_mod1[25]

dem_shortrun <- coef(model_2)["dem"]
lag1_mod2 <- coef(model_2)[2]
lag2_mod2 <- coef(model_2)[3]
effect1 <- dem_shortrun
effect2 <- (effect1 * lag1_mod2) + dem_shortrun
effect3 <- (effect2 * lag1_mod2) +
  (effect1 * lag2_mod2) +
  dem_shortrun
effects_mod2 <- c(effect1, effect2, effect3)

for (i in 4:30) {
  eff <- (effects_mod2[i-1] * lag1_mod2) +
    (effects_mod2[i-2] * lag2_mod2) +
    dem_shortrun
  effects_mod2 <- c(effects_mod2, eff)
}
eff_25_2 <- effects_mod2[25]

dem_shortrun <- coef(model_3)["dem"]
lag1_mod3 <- coef(model_3)[2]
lag2_mod3 <- coef(model_3)[3]
lag3_mod3 <- coef(model_3)[4]
lag4_mod3 <- coef(model_3)[5]
effect1 <- dem_shortrun
effect2 <- (effect1 * lag1_mod3) + dem_shortrun
effect3 <- (effect2 * lag1_mod3) +
  (effect1 * lag2_mod3) +
  dem_shortrun
effect4 <- (effect3 * lag1_mod3) +
  (effect2 * lag2_mod3) +
  (effect1 * lag3_mod3) +
  dem_shortrun
effects_mod3 <- c(effect1, effect2, effect3, effect4)

for (i in 5:30) {
  eff <- (effects_mod3[i-1] * lag1_mod3) +
    (effects_mod3[i-2] * lag2_mod3) +
    (effects_mod3[i-3] * lag3_mod3) +
    (effects_mod3[i-4] * lag4_mod3) +
    dem_shortrun
  effects_mod3 <- c(effects_mod3, eff)
}
eff_25_3 <- effects_mod3[25]

dem_shortrun <- coef(model_4)["dem"]
lag1_mod4 <- coef(model_4)[2]
lag2_mod4 <- coef(model_4)[3]
lag3_mod4 <- coef(model_4)[4]
lag4_mod4 <- coef(model_4)[5]
lag5_mod4 <- coef(model_4)[6]
lag6_mod4 <- coef(model_4)[7]
lag7_mod4 <- coef(model_4)[8]
lag8_mod4 <- coef(model_4)[9]
effect1 <- dem_shortrun
effect2 <- (effect1 * lag1_mod4) + dem_shortrun
effect3 <- (effect2 * lag1_mod4) +
  (effect1 * lag2_mod4) +
  dem_shortrun
effect4 <- (effect3 * lag1_mod4) +
  (effect2 * lag2_mod4) +
  (effect1 * lag3_mod4) +
  dem_shortrun
effect5 <- (effect4 * lag1_mod4) +
  (effect3 * lag2_mod4) +
  (effect2 * lag3_mod4) +
  (effect1 * lag4_mod4) +
  dem_shortrun
effect6 <- (effect5 * lag1_mod4) +
  (effect4 * lag2_mod4) +
  (effect3 * lag3_mod4) +
  (effect2 * lag4_mod4) +
  (effect1 * lag5_mod4) +
  dem_shortrun
effect7 <- (effect6 * lag1_mod4) +
  (effect5 * lag2_mod4) +
  (effect4 * lag3_mod4) +
  (effect3 * lag4_mod4) +
  (effect2 * lag5_mod4) +
  (effect1 * lag6_mod4) +
  dem_shortrun
effect8 <- (effect7 * lag1_mod4) +
  (effect6 * lag2_mod4) +
  (effect5 * lag3_mod4) +
  (effect4 * lag4_mod4) +
  (effect3 * lag5_mod4) +
  (effect2 * lag6_mod4) +
  (effect1 * lag7_mod4) +
  dem_shortrun
effects_mod4 <- c(effect1, effect2, effect3, effect4,
                  effect5, effect6, effect7, effect8)

for (i in 9:30) {
  eff <- (effects_mod4[i-1] * lag1_mod4) +
    (effects_mod4[i-2] * lag2_mod4) +
    (effects_mod4[i-3] * lag3_mod4) +
    (effects_mod4[i-4] * lag4_mod4) +
    (effects_mod4[i-5] * lag5_mod4) +
    (effects_mod4[i-6] * lag6_mod4) +
    (effects_mod4[i-7] * lag7_mod4) +
    (effects_mod4[i-8] * lag8_mod4) +
    dem_shortrun
  effects_mod4 <- c(effects_mod4, eff)
}
eff_25_4 <- effects_mod4[25]

eff_25 <- round(
  c(eff_25_1, eff_25_2, eff_25_3, eff_25_4),
  3
)
print(eff_25)

se1 <- sqrt(diag(vcov(model_1)))
se2 <- sqrt(diag(vcov(model_2)))
se3 <- sqrt(diag(vcov(model_3)))
se4 <- sqrt(diag(vcov(model_4)))

override.coef.1 <- c(
  coef(model_1)["dem"],
  coef(model_1)["lag1"],
  NA, NA, NA, NA, NA, NA, NA
)
override.se.1 <- c(
  se1["dem"],
  se1["lag1"],
  NA, NA, NA, NA, NA, NA, NA
)

override.coef.2 <- c(
  coef(model_2)["dem"],
  coef(model_2)["lag1"],
  coef(model_2)["lag2"],
  NA, NA, NA, NA, NA, NA
)
override.se.2 <- c(
  se2["dem"],
  se2["lag1"],
  se2["lag2"],
  NA, NA, NA, NA, NA, NA
)

override.coef.3 <- c(
  coef(model_3)["dem"],
  coef(model_3)["lag1"],
  coef(model_3)["lag2"],
  coef(model_3)["lag3"],
  coef(model_3)["lag4"],
  NA, NA, NA, NA
)
override.se.3 <- c(
  se3["dem"],
  se3["lag1"],
  se3["lag2"],
  se3["lag3"],
  se3["lag4"],
  NA, NA, NA, NA
)

override.coef.4 <- c(
  coef(model_4)["dem"],
  coef(model_4)["lag1"],
  coef(model_4)["lag2"],
  coef(model_4)["lag3"],
  coef(model_4)["lag4"],
  coef(model_4)["lag5"],
  coef(model_4)["lag6"],
  coef(model_4)["lag7"],
  coef(model_4)["lag8"]
)
override.se.4 <- c(
  se4["dem"],
  se4["lag1"],
  se4["lag2"],
  se4["lag3"],
  se4["lag4"],
  se4["lag5"],
  se4["lag6"],
  se4["lag7"],
  se4["lag8"]
)
```

### Tabulation

```{r}
models <- list(model_1, model_2, model_3, model_4)

texreg(
  models,
  override.coef = list(
    override.coef.1,
    override.coef.2,
    override.coef.3,
    override.coef.4
  ),
  override.se = list(
    override.se.1,
    override.se.2,
    override.se.3,
    override.se.4
  ),
  custom.model.names = c(
    "(1)", "(2)", "(3)", "(4)"
  ),
  custom.coef.names = c(
    "Democracy", "Lag 1", "Lag 2",
    "Lag 3", "Lag 4", "Lag 5",
    "Lag 6", "Lag 7", "Lag 8"
  ),
  custom.gof.rows = list(
    "Persistence"          = pers,
    "Long run effect"      = lre,
    "Effect after 25 years" = eff_25
  ),
  file = "output/table_2_FE.tex",
  caption = "Effect of Democracy on (Log) GDP per Capita"
)
```

\input{output/table_2_FE.tex}

\input{output/TableMain_GMM.tex}

## Figure.2

## Table.3

## Table.4

## Table.5

# Extention


