---
title: 'Data Management & Analysis Final Project'
subtitle: 'Replication and Extention for Acemoglu, Naidu, Restrepo and Robinson (2019)'
author: 
  - "(Name:) (University ID:) "
  - "(Name:) (University ID:) "
date: "(Submission Due:) 2025/02/06"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
    number_sections: true
  word_document:
    toc: true
    toc_depth: 3
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{float}
  - \usepackage[table]{xcolor}
---

\newpage

## Setup
  
```{r setup, echo=TRUE, cache=FALSE, warning=FALSE, message=FALSE}
pacman::p_load(
  rmdformats,
  knitr,
  tinytex,
  haven,
  tidyverse,
  kableExtra
)

## Global options
options(max.print="75")
opts_chunk$set(fig.align="center",
               echo=TRUE,
               cache=TRUE,
               prompt=FALSE,
               tidy=FALSE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

# About this Report

## Project Type

## Summary of the Paper

### What the problem is

### Why it is important

### How you solve the problem

### What we find

## Data

```{r}
data <- read_dta("data/raw/DDCGdata_final.dta")

# Define the function to summarize the data
summarize_data <- function(data, n = 10) {
  cat("Sample size (number of rows):", nrow(data), "\n")
  cat("Number of variables (columns):", ncol(data), "\n")
  cat("Variable names (first", n, "names):\n")
  print(head(colnames(data), n))
}

summarize_data(data)
```

## Empirical Methods

### Event Study (Figure.1)

### Dynamic Panel Data Model (Table.2)

# Replication

## Figure.1

### Preprocessing

```{r}
# Rename '_ID' to 'id', sort by year within each id, then ungroup
data_f1 <- data %>%
  rename(id = "_ID") %>%
  group_by(id) %>%
  arrange(year) %>%
  ungroup()

# For each id, create a lagged democracy indicator and define the transition:
# - Transition = 1 if it goes from 0 to 1 (non-democracy to democracy)
# - Transition = 0 if it remains at 0 (non-democracy)
# - Otherwise, transition is set to NA
data_f1 <- data_f1 %>%
  group_by(id) %>%
  arrange(year) %>%
  mutate(prev_dem = lag(dem, 1)) %>%  
  ungroup() %>%
  mutate(transition = case_when(
    dem == 1 & prev_dem == 0 ~ 1,
    dem == 0 & prev_dem == 0 ~ 0,
    TRUE ~ NA_real_
  ))

# Compute lags for 'y' (lags 1 through 4) within each id and filter out rows 
# with any missing lag values
data_f1 <- data_f1 %>%
  group_by(id) %>%
  arrange(year) %>%
  mutate(
    lag1 = lag(y, 1),
    lag2 = lag(y, 2),
    lag3 = lag(y, 3),
    lag4 = lag(y, 4)
  ) %>%
  ungroup() %>%
  filter(!is.na(lag1) & !is.na(lag2) & !is.na(lag3) & !is.na(lag4))

# Calculate GDP differences for past periods:
# For t from -15 to -2, create columns 'gdpDiff_m[abs(t)]' as the difference 
# between the lagged 'y' (by abs(t)) and lag1
for (t in -15:-2) {
  col_name <- paste0("gdpDiff_m", abs(t))
  data_f1 <- data_f1 %>%
    group_by(id) %>%
    arrange(year) %>%
    mutate(!!col_name := lag(y, abs(t)) - lag1) %>%
    ungroup()
}

# Set the GDP difference for the immediate past period (m1) to 0
data_f1 <- data_f1 %>%
  mutate(gdpDiff_m1 = 0)

# Compute the GDP difference for the current period (0) 
# as the difference between 'y' and lag1
data_f1 <- data_f1 %>%
  group_by(id) %>%
  arrange(year) %>%
  mutate(gdpDiff_0 = y - lag1) %>%
  ungroup()

# Calculate GDP differences for future periods:
# For t from 1 to 30, create columns 'gdpDiff_p[t]' 
# as the difference between the lead of 'y' (by t) and lag1
for (t in 1:30) {
  col_name <- paste0("gdpDiff_p", t)
  data_f1 <- data_f1 %>%
    group_by(id) %>%
    arrange(year) %>%
    mutate(!!col_name := lead(y, t) - lag1) %>%
    ungroup()
}

# Keep only rows where the transition value is not missing
data_f1 <- data_f1 %>% filter(!is.na(transition))
```

### Estimation

```{r}
# Define a function to estimate the Average Treatment Effect on the Treated (ATET)
estimateATET <- function(outcome_col) {
  # Filter out rows with missing outcome or transition values
  sub_data <- data_f1 %>% filter(!is.na(.data[[outcome_col]]), !is.na(transition))
  if(nrow(sub_data) == 0) return(NA)
  
  # Create a factor for 'year' with sorted levels
  year_levels <- sort(unique(sub_data$year))
  sub_data <- sub_data %>% mutate(year_factor = factor(year, levels = year_levels))
  
  # Split the data into control (transition == 0) and treated (transition == 1) groups
  control_data <- sub_data %>% filter(transition == 0)
  treated_data <- sub_data %>% filter(transition == 1)
  
  # Return NA if the control group lacks sufficient observations or year variation
  if(nrow(control_data) < 2 || length(unique(control_data$year)) < 2) return(NA)
  
  # Fit a linear model on the control group with year dummies (without intercept)
  model_formula <- as.formula(paste(outcome_col, "~ year_factor - 1"))
  control_model <- tryCatch(lm(model_formula, data = control_data),
                            error = function(e) NULL)
  if(is.null(control_model)) return(NA)
  
  # Predict outcomes for the treated group using the control model
  predicted_outcomes <- tryCatch(predict(control_model, newdata = treated_data),
                                 error = function(e) rep(NA, nrow(treated_data)))
  
  # Compute treatment effects as the difference between actual and predicted outcomes
  treatment_effects <- treated_data[[outcome_col]] - predicted_outcomes
  
  # Return the mean treatment effect on the treated (ATET)
  mean(treatment_effects, na.rm = TRUE)
}

# Define relative time periods: pre-treatment (-15 to -1) and post-treatment (0 to 30)
relative_times <- c(seq(-15, -1), seq(0, 30))
atets <- numeric(length(relative_times))

# Loop over each relative time period to estimate ATET for the corresponding outcome column
for(i in seq_along(relative_times)) {
  t_val <- relative_times[i]
  # Set the column name based on whether the period is before (m), during (0), 
  # or after (p) treatment
  if(t_val < 0) {
    col_name <- paste0("gdpDiff_m", abs(t_val))
  } else {
    col_name <- if(t_val == 0) "gdpDiff_0" else paste0("gdpDiff_p", t_val)
  }
  atets[i] <- estimateATET(col_name)
}

# Create a data frame with the relative time periods and their corresponding ATET estimates
results_df <- data.frame(RelativeTime = relative_times, ATET = atets)
```

### Plot

```{r}
figure_1 <- ggplot(results_df, aes(x = RelativeTime, y = ATET)) +
  geom_line(color = "black") +
  scale_x_continuous(breaks = seq(-15, 30, 5)) +
  labs(x = "Years around Democratization", 
       y = "Change in GDP per capita (log points)") +
  theme_bw()

ggsave("output/figure_1.pdf", width = 14, height = 8, units = "cm")
```

![Event Study](output/figure_1.pdf)

## Table.1

```{r}
# Define variable names and display labels
var_info <- tibble(
  var = c("gdppercapitaconstant2000us",  # data column name
          "ginv",
          "tradewb",
          "prienr",
          "secenr",
          "taxratio",
          "mortnew",
          "unrestn",
          "marketref"),
  label = c("GDP per capita",           # table label
            "Investment share of GDP",
            "Trade share of GDP",
            "Primary-school enrollment rate",
            "Secondary-school enrollment rate",
            "Tax revenue share of GDP",
            "Child mortality per 1,000 births",
            "Unrest rate",
            "Market reforms index (0–100)")
)

# Calculate descriptive statistics
calc_summary <- function(df, var, group_var) {
  df %>%
    filter(!is.na(.data[[var]])) %>%       # remove NAs
    group_by({{ group_var }}) %>%
    summarise(
      Observations = n(),                 # count
      Mean         = mean(.data[[var]], na.rm = TRUE),
      SD           = sd(.data[[var]], na.rm = TRUE),
      .groups      = "drop"
    ) %>%
    mutate(Variable = var)                # record variable name
}

# List of variables to summarize
var_list <- var_info$var

# Summarize variables, reshape by democracy status, and add labels
summary_table <- lapply(var_list, function(x) calc_summary(data, x, dem)) %>%
  bind_rows() %>%
  pivot_wider(
    names_from  = dem, 
    values_from = c(Observations, Mean, SD),
    names_glue  = "{.value}_dem{dem}"
  ) %>%
  # Rename columns for clarity
  rename(
    Observations_Nondem = Observations_dem0,
    Mean_Nondem         = Mean_dem0,
    SD_Nondem           = SD_dem0,
    Observations_Dem    = Observations_dem1,
    Mean_Dem            = Mean_dem1,
    SD_Dem              = SD_dem1
  ) %>%
  # Join with var_info to add labels
  left_join(var_info, by = c("Variable" = "var")) %>%
  # Rearrange columns and use label as Variable
  select(label,
         Observations_Nondem, Mean_Nondem, SD_Nondem,
         Observations_Dem,    Mean_Dem,    SD_Dem
  ) %>%
  rename(Variable = label)

# Format table for PDF output with a multi-column header
colnames(summary_table) <- c("Variable",
                             "Observations", "Mean", "SD",
                             "Observations", "Mean", "SD")

latex_table <- summary_table %>%
  kbl(
    caption = "Summary Statistics by Democracy Status",
    format = "latex",
    booktabs = TRUE,
    digits = 2
  ) %>%
  add_header_above(c(" " = 1, "Nondemocracies" = 3, "Democracies" = 3)) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))

# Save the table as a TeX file
save_kable(latex_table, file = "output/table_1.tex")
```

\input{output/table_1.tex}

## Table.2

## Figure.2

## Table.3

## Table.4

## Table.5

# Extention


